Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-29 ms.tex
more minor clean-up in discussion of predicting Planck observations

\subsection{Predicting the Observed SED}
With the formalism established in $\S$\ref{sec:modeling} and 
$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
MCMC sampling to predict the observed SED, which we will denote by 
\{$\tilde{I}_{\nu_i}$\}. The predicted broadband intensities are given by:

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
$K_{CMB}$ to MJy/sr:

>>>>

\subsection{Predicting the Observed SED}
With the formalism established in $\S$\ref{sec:modeling} and 
$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
MCMC sampling to predict the observed SED, which we will denote by 
\{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
$K_{CMB}$ to MJy/sr:
